Oral Manuscript

### 2018-06-12 index.Rmd
reduced font

--- 
title: "Oral Manuscript"
author: "Matt Galloway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
#bibliography: [lib.bib, packages.bib]
bibliography: lib.bib
biblio-style: apalike
colorlinks: yes
lot: no
lof: no
fontsize: 12pt
link-citations: yes
#url: 'https://mgallow.github.io/oral_manuscript/'
github-repo: MGallow/oral_manuscript
description: "This is a working manuscript in preparation for Matt Galloway's doctoral oral examination."
---

>>>>

--- 
title: "Oral Manuscript"
author: "Matt Galloway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
#bibliography: [lib.bib, packages.bib]
bibliography: lib.bib
biblio-style: apalike
colorlinks: yes
lot: no
lof: no
fontsize: 11pt
link-citations: yes
#url: 'https://mgallow.github.io/oral_manuscript/'
github-repo: MGallow/oral_manuscript
description: "This is a working manuscript in preparation for Matt Galloway's doctoral oral examination."
---
